Price of Anarchy for Mean Field Games

### 2018-08-05 PoA.tex
minor edits, moved observation earlier because it is used in Prop 1

\subsection{\textbf{Theoretical Results}}
For the remainder of the paper, we assume the coefficients are independent of time and non-negative:
\begin{equation*}
    (b_1(t),\bar{b}_1(t),b_2(t),\bar{b}_2(t),q(t),\bar{q}(t),r(t),\bar{r}(t),s(t),\bar{s}(t))=(b_1,\bar{b}_1,b_2,\bar{b}_2,q,\bar{q},r,\bar{r},s,\bar{s})\in (\mathbb{R}^+)^{10},
\end{equation*}
$$    (q_T,\bar{q}_T,s_T)\in(\mathbb{R}^+)^{3},$$
and therefore,
\begin{equation*}
\begin{split}
    \left(a^{MFG}(t), b^{MFG}(t), c^{MFG}(t) \right)&=\left(a^{MFG}, b^{MFG}, c^{MFG} \right) \\
    \left(a^{MKV}(t), b^{MKV}(t), c^{MKV}(t) \right)&=\left(a^{MKV}, b^{MKV}, c^{MKV}\right).
\end{split}
\end{equation*}
Also, it will be convenient to denote:
\begin{equation}
\lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})},  \qquad u_t := \lambda \bar{\eta}_t^{MFG}, \qquad w_t := \bar{\eta}_t^{MKV}.
\label{eq:lambda}
\end{equation}

@@

\begin{proof}
    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), and using the fact that $b^{MFG}-b^{MKV}=c^{MFG}-c^{MKV}$, the result is clear.
\end{proof}

\begin{remark}
	Recall from Remark \ref{remark_2} that in the standard mean field game, $\bar{b}_2=\bar{r}=0$, and thus, $\lambda=1$. Although Proposition \ref{prop: lq_subtract_FBSDEs} is a simple result, we will see shortly in Corollary \ref{corollary_3} that in the case when $\lambda=1$, the sufficient condition given by equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3}) is also a necessary condition to have $PoA=1$. We can see that in the standard mean field game setting, Proposition \ref{prop: lq_subtract_FBSDEs} is similar to Theorem 3.4 in \cite{pierre_poa} which characterizes the global efficiency of MFG equilibria in case of separated Hamiltonian. See also Remark 6.1 in \cite{nourian2013nash} for a flocking model.
\end{remark}

@@

To compute the price of anarchy, it is useful to make the following observations:
a^{MFG}=a^{MKV}=:a, \qquad
\eta_t^{MFG} = \eta_t^{MKV}=:\eta_t, \qquad
v_t^{MFG}=v_t^{MKV}=:v_t,
we can rewrite:

@@

then we use the integration by parts for the first term in the bracket:

@@

Finally, we solve:

>>>>

\subsection{\textbf{Theoretical Results}}
For the remainder of the paper, we assume the coefficients are independent of time and non-negative:
\begin{equation*}
    (b_1(t),\bar{b}_1(t),b_2(t),\bar{b}_2(t),q(t),\bar{q}(t),r(t),\bar{r}(t),s(t),\bar{s}(t))=(b_1,\bar{b}_1,b_2,\bar{b}_2,q,\bar{q},r,\bar{r},s,\bar{s})\in (\mathbb{R}^+)^{10},
\end{equation*}
$$    (q_T,\bar{q}_T,s_T)\in(\mathbb{R}^+)^{3},$$
and therefore,
\begin{equation*}
\begin{split}
    \left(a^{MFG}(t), b^{MFG}(t), c^{MFG}(t) \right)&=\left(a^{MFG}, b^{MFG}, c^{MFG} \right) \\
    \left(a^{MKV}(t), b^{MKV}(t), c^{MKV}(t) \right)&=\left(a^{MKV}, b^{MKV}, c^{MKV}\right).
\end{split}
\end{equation*}
Also, it will be convenient to denote:
\begin{equation}
\lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})},  \qquad u_t := \lambda \bar{\eta}_t^{MFG}, \qquad w_t := \bar{\eta}_t^{MKV}.
\label{eq:lambda}
\end{equation}
and to make the following observations:
\begin{equation}
a^{MFG}=a^{MKV}=:a, \qquad
\eta_t^{MFG} = \eta_t^{MKV}=:\eta_t, \qquad
v_t^{MFG}=v_t^{MKV}=:v_t.
\label{eq:observations}
\end{equation}

@@

\begin{proof}
    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), and using the fact that $a^{MFG}=a^{MKV}$ and $b^{MFG}-b^{MKV}=c^{MFG}-c^{MKV}$, the result is clear.
\end{proof}

\begin{remark}
	Recall from Remark \ref{remark_2} that in the standard mean field game, $\bar{b}_2=\bar{r}=0$, and thus, $\lambda=1$. Although Proposition \ref{prop: lq_subtract_FBSDEs} is a simple result, we will see shortly in Corollary \ref{corollary_3} that in the case when $\lambda=1$, the sufficient condition given by equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3}) is also a necessary condition to have $PoA=1$. We can see that in the standard mean field game setting, Proposition \ref{prop: lq_subtract_FBSDEs} is similar to Theorem 3.4 in \cite{pierre_poa} which characterizes the global efficiency of MFG equilibria in the case of a separated Hamiltonian. See also Remark 6.1 in \cite{nourian2013nash}, where it is noted that the mean field game and control of McKean-Vlasov type problems are the same for a particular model of flocking.
\end{remark}

@@

Using the observations in equation (\ref{eq:observations}), we can rewrite:

@@

then using integration by parts for the first term in the bracket:

@@

Finally, we arrive at:
